Finite Property Convex Elicitation Notes

### 2019-01-17 jessie-writeup/jw-holes-clarified.tex
Added written proofs for why abstain should not be 3 embeddable on 9 outcomes

\begin{theorem}[F/K 2014] \label{thm:bij-loss-to-score}
	Let $\Gamma: \P \toto\R$ be nonredundant and elicited by $\Gamma$-regular \jessiet{Can we assume this with convexity?} affine loss $A: \R \times \P \to \reals$ be given.
	Then $L$ elicits $\Gamma$ if and only if there exists some convex $G: \conv(\P) \to \reals$ with $G(\P) \subseteq \reals$, some $\D \subseteq \partial G$, and a bijection $\varphi : \R \to \D$ so that $\Gamma(t) = \varphi^{-1}(\D \cap \partial G_t)$.
\end{theorem}

>>>>

\begin{theorem}[F/K 2014] \label{thm:bij-loss-to-score}
	Let $\Gamma: \P \toto\R$ be nonredundant and elicited by $\Gamma$-regular \jessiet{Can we assume this with convex elicitability? I read $\Gamma$-regular to mean that $L(r,p) < \infty$ for all $r \in \R$.} affine loss $L: \R \times \P \to \reals$ be given.
	Then $L$ elicits $\Gamma$ if and only if there exists some convex $G: \conv(\P) \to \reals$ with $G(\P) \subseteq \reals$, some $\D \subseteq \partial G$, and a bijection $\varphi : \R \to \D$ so that $\Gamma(t) = \varphi^{-1}(\D \cap \partial G_t)$.
\end{theorem}

\begin{corollary}
	Let the $\Gamma$-regular convex function $L$ elicit $\Gamma:\P \toto \R$.
	\jessie{TODO: want to be able to argue that once we reduce to equivalent reports, there is a bijection between subgradients of the score and reports in $\R'$.}
%	The set $\D \subseteq \partial G_p$ is finite if and only if $\R$ is finite.
%	There is a finite set $\D \subseteq \partial G_t$ so that $\Gamma(p) = \varphi^{-1}(\D \cap \partial G_t)$ is finite if and only if there is a finite set $\R' \subseteq \R$ so that there is a bijection from $\phi: \R'\to \D$.
\end{corollary}
\begin{proof}
\end{proof}
